Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-02-02 Documents/Talk/content.tex
Small edits
More figs etc

\begin{frame}[t]{Diffusive Nested Sampling}
\begin{columns}[T]
\begin{column}{0.35\textwidth}
  \vspace{30pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item Replace the posterior distribution with a {\bf mixture of constrained priors}
  \item Can cross valleys (the prior is a mixture component)
  \item Posterior is available via re-weighting
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.5\textwidth}
  \hspace{50pt}
  \includegraphics[scale=0.4]{dnest.png}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}[t]{Hyperparameters}
\begin{center}
\includegraphics[scale=0.3]{StarFieldFigures/inference2.pdf}
\end{center}
\end{frame}

@@

\begin{frame}[t]{Recommendations}
It is infeasable to apply this approach wholesale.
Instead I would use it on small subsets of imaging that are of specific interest.
\end{frame}

@@

>>>>

\begin{frame}[t]{Diffusive Nested Sampling}
\begin{columns}[T]
\begin{column}{0.35\textwidth}
  \vspace{10pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item Replace the posterior distribution with a {\bf mixture of constrained priors}
  \item Can cross valleys (the prior is a mixture component)
  \item Posterior is available via re-weighting
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.5\textwidth}
  \hspace{50pt}
  \includegraphics[scale=0.4]{dnest.png}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}[t]{Hyperparameters}
\begin{center}
\includegraphics[scale=0.28]{StarFieldFigures/inference2.pdf}
\end{center}
\end{frame}

@@

\begin{frame}[t]{Recommendations}
It is infeasible to apply this approach wholesale.
Instead I would use it on small subsets of imaging that are of specific interest.

\begin{center}
{\it Any takers?}
\end{center}
\end{frame}

@@

\begin{frame}[t]{Exoplanets: Simulated Dataset Results}
The true value was $N$=7.
\begin{center}
\includegraphics[scale=0.35]{ExoplanetFigures/fake_data_N.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Exoplanets: Simulated Dataset Results}
This is the posterior distribution for $P_1$. Keep in mind the {\bf
label-switching degeneracy}.
\begin{center}
\includegraphics[scale=0.35]{ExoplanetFigures/fake_data_periods.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Exoplanets: Simulated Dataset Results}
Here, we can see why one of the planets was not ``detected'':
\begin{center}
\includegraphics[scale=0.35]{ExoplanetFigures/fake_data_posterior.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Time}
It takes about 15-20 minutes to obtain some posterior samples.

Compare with Phil Gregory's code (30 minutes per planet, no trans dimensional
moves).
\end{frame}

\begin{frame}[t]{Gliese 581}
Gliese 581 is an M dwarf which has been observed extensively with the HARPS
and UVES spectrographs.

There is controversy about $N$, some people only
believe {\bf two} of the claimed planets, while other analyses suggest
{\bf up to 6} (with a few of these in the habitable zone).
\end{frame}

\begin{frame}[t]{Giant Disclaimer}
\begin{center}
\includegraphics[scale=0.25]{robertson.png}
\end{center}
\end{frame}

\begin{frame}[t]{Giant Disclaimer}
\begin{center}
\includegraphics[scale=0.25]{robertson.png}
\end{center}
\end{frame}
